Using reference models in variable selection \vspace{.1in}

### 2020-04-22 paper/ref_approach.tex

Using the data generating mechanism \eqref{eq:simulated_data}, we
simulate data sets of different sizes with a relatively large number
of variables $p=100$ with $k=20$ of them being predictive.  We compare
the minimal subset variable selection perfomance of projection
predictive approach (with a reference model), a Bayesian stepwise
forward selection with and without a reference model, and maximum
likelihood stepwise forward selection with and without a reference
model:
\begin{itemize}
\item projpred: The projective prediction approach is used. 
  The reference model is a Bayesian linear regression
  model using the first five supervised principal components \citep{piironen2018} as predictors
  and the full posterior predictive distribution as the basis of the projection.   
  The search heuristic  is forward search and the predictive performance 
  is estimated via 10-fold cross-validation.

@@

\item Choose the smallest submodel (size) that is sufficiently close to the reference model's predictive utility score.

@@

In general, Expression \eqref{eq:draw_by_draw} is not an easy optimisation problem
However, in the special case of the submodels being
generalised linear models with a likelihood coming from the exponential family, \eqref{eq:draw_by_draw} reduces to a
maximum likelihood estimation problem, which can be easily solved
\citep{paper:original_proj}. For further details on the projective
prediction workflow and implementation see paper by \citet{paper:projpred}.

>>>>

Using the data generating mechanism \eqref{eq:simulated_data}, we
simulate data sets of different sizes with a relatively large number
of variables $p=100$ with $k=20$ of them being predictive.  We compare
the minimal subset variable selection perfomance of projection
predictive approach (with a reference model), a Bayesian stepwise
forward selection with and without a reference model, and maximum
likelihood stepwise forward selection with and without a reference
model:
\begin{itemize}
\item projpred: The projective prediction approach is used. 
  The reference model is a Bayesian linear regression
  model using the first five supervised principal components \citep{piironen2018} as predictors
  and the full posterior predictive distribution as the basis of the projection.   
  The search heuristic  is forward search and the predictive performance 
  is estimated via 10-fold cross-validation. The selection continues
  until the predictive performance is close to the predictive
  performance of the reference model. See more details in Appendix A.

@@

\item Choose the smallest submodel (size) that is sufficiently close to the reference model's predictive utility score. The results in this paper were not sensitive to the specific choice of how ``sufficiently close'' is defined, and we used the same definition as \citet{paper:projpred}.

@@

In general, Expression \eqref{eq:draw_by_draw} is not an easy optimisation problem
However, in the special case of the submodels being
generalised linear models with a likelihood coming from the exponential family, \eqref{eq:draw_by_draw} reduces to a
maximum likelihood estimation problem, which can be easily solved
\citep{paper:original_proj}. For further details on the projective
prediction workflow and implementation see the paper by \citet{paper:projpred}.
